\documentclass[twocolumn,a4paper]{article}
\usepackage{hyperref}
\hypersetup{
linktoc=all,     %set to all if you want both section*s and subsections linked
colorlinks=true, %set true if you want colored links
linkcolor=black,  %choose some color if you want links to stand out
}

\begin{document}
\title{List of Item Descriptions for \emph{Dark Souls: The Board Game}}
\date{}
\maketitle
\tableofcontents %The document has to be compiled to times for the TOC to work properly.

\part{Starting Equipment}
\section*{Assassin}
\paragraph{Assassin's Armor}
Soft leather armor worn by assassins who lurk in the shadows.\\
The thick leather offers reasonable absorption without creating any undesired noise. A well-crafted piece of protection.\\
Critical spots are reinforced with metal.
\paragraph{Estoc}
The largest of the thrusting swords. Can pierce an armored knight in one thrust.\\
The blade is also sharp, allowing slicing as well.
\paragraph{Target Shield}
Small round metal shield. Four protrusions used to parry attacks.\\
Small shields are always less stable, but landing critical hits after parry is easier. This shield is specialized for parrying.
\section*{Herald}
\paragraph{Herald Armor}
Steel armor with a pure white cape, the signature of Heralds of the way of White.\\
Protection made of steel has excellent physical absorption, but is found lacking against blunt strikes and lightning damage.
\paragraph{Kite Shield}
An orthodox metal shield.\\
Medium shields are the most average of shields, providing a practical balance of damage absorption, stability and weight.
\paragraph{Spear}
Standard spear used commonly by soldiers. Long reach, and can be used with shield up. Effective against hard exteriors, and can hit for high damage at the right moment of an enemy's swing. But the hit radius is small, and it is easily blocked by shields.
\paragraph{Talisman}
Medium for casting miracles of the Gods. Standard talisman issued to common believers. Equip talisman to cast miracles. Attune miracles from a scroll at a bonfire. Most miracles have a limited no. of uses.
\section*{Knight}
\paragraph{Kite Shield}
An orthodox metal shield.\\
Medium shields are the most average of shields, providing a practical balance of damage absorption, stability and weight.
\paragraph{Knight Armor}
Armor of a lower-rank knight. Despite the thin metal used, the grooved texture gives it added protection.
\paragraph{Long Sword}
A balanced, widely-used standard straight sword.\\
Inflicts reliable standard damage, as well as high thrust damage.
\section*{Warrior}
\paragraph{Northern Armor}
Iron armor of a stalwart northern warrior. Supported by interwoven chainmail.\\
Iron defensive wear grants superior absorption. Being from the north, it should also offer resistance to the cold. \paragraph{Battle Axe}
Standard battle axe. Inflicts regular damage, making it effective in various situations.\\
Powerful attack due to its weight, but one wrong swing leaves the wielder open, so timing and proximity to the enemy must be judged carefully.
\paragraph{Round Shield}
Standard round wooden shield.\\
Wooden shields are light, manageable, and offer relatively high magic absorption.

\newpage
\part{Class Treasures}
\section*{Assassin}
\paragraph{Composite Bow}
Composite bow emphasizing power. Requires more strength than standard bows.\\
However, its range is shorter, making it unfit for sniping.
\paragraph{Hornet Ring}
One of the special rings granted to the four knights of Gwyn. The Hornet Ring belonged to the Lord's Blade Ciaran.\\
By boosting critical attacks, its wearer can annihilate foes, as Ciaran's dagger laid waste to Lord Gwyn's enemies.
\paragraph{Rotten Ghru Dagger}
A crude, half-rotten dagger.\\
Choice weapon of the blunt-horned Ghrus, descendants of the acolytes of Farron Keep.\\
The rancid blade is drenched in rotten waste, making it acutely poisonous.
\paragraph{Shadow Armour}
Black cloth garb worn by spooks from an Eastern land. Designed so as not to hinder their unique form of martial arts.\\
While it sacrifices defense for the sake of greater mobility, it does offer resistance to bleeding and poison among other things, perhaps due to the nature of espionage.
\paragraph{Spotted Whip}
Whip born from the soul of the Demon of Song. Covered with strange spots that betray its poisonous effects.\\
The Demon's sonorous voice in stark contrast to its hideous form, is surely intended to lure people close so that it may devour them.
\pagebreak %f
\section*{Herald}
\paragraph{Cathedral Knight Armour}
Massive iron armor worn by knights serving the Cathedral of the Deep.\\
Repulsive creatures of the deep are sure to attract the foolish, but the cathedral knights are prepared to meet such intruders head on with their more than ample might.
\paragraph{Golden Wing Crest Shield}
A blue knight's shield engraved with a golden wing crest.\\
This shield is exceptional amongst the enchanted blue shields; not only does it boast high magic absorption, but also enables its wielder to parry spells.
\paragraph{Lothric's Holy Sword}
Prince Lothric's straight sword, blessed by Emma with potent magic.\\
Young Lothric was meant to be a champion, and was expected to wield this platinum sword, but some things will remain distant dreams forever.
\paragraph{Replenishment}
Common miracle amongst cleric knights. Gradual HP restoration.\\
Beware of the cleric knight blessed by Replenishment, for he shall not fall easily.
\paragraph{Tiny Being's Ring}
Ring made of an ancient tiny red jewel. Grants small increase to HP.\\
Rings grant powers large and small. Their discovery, and effective use, can make one's journey easier.
\section*{Knight}
\paragraph{Blue Tearstone Ring}
The rare gem called tearstone has the uncanny ability to sense imminent death.\\
This blue tearstone from Catarina boosts the defence of its wearer when in danger.
\paragraph{Broadsword}
An accessible sword which inflicts consistent regular damage and high slash damage, making it applicable to a variety of situations.\\
The horizontal sweeping motion makes this sword effective against multiple enemies.
\paragraph{Lothric Knight Armour}
Armor of a celebrated Lothric knight.
The coat of distinction is all but fallen apart.\\
The Knight has served as one of the Three Pillars since ancient times, and shares place alongside the wyverns as a symbol of Lothric.\\
Only those possessing a knight's resolve are fit to wear this garment.
\paragraph{Spider Shield}
Shield of the savage mountain bandits. Uniquely-shaped with a large black spider etched upon it.\\
Has resistance to poison.
\paragraph{Sun Princess Ring}
Ring associated with Gwynevere, princess of sunlight and eldest daughter of Gwyn, the First Lord.\\
The ring is vaguely warm, like a beam of sunlight, and gradually restores HP.\\
Gwynevere left her home with a great many other deities, and became a wife and a mother, raising several heavenly children.
\section*{Warrior}
\paragraph{Caestus}
The weapon augments one's bare hands with thick, studded leather.\\
The Caestus has a short reach, but quickly cools down. Amount of damage inflicted is dependent on its wearer's strength.
\paragraph{Great Wooden Hammer}
This giant wooden hammer is a worker's tool in the Undead Settlement.\\
Intended to grind flesh and bone to prepare for burial, rather than use in battle.
\paragraph{Knight Slayer's Ring}
Ring of the savage Tsorig, more commonly known as the Knight Slayer.\\
Enemies lose more stamina when guarding attacks.\\
Long ago, Tsorig engaged the guardians of an ancient city in a bloody confrontation, and returned with their rings as his prize, still frozen on their dismembered fingers.
\pagebreak %f
\paragraph{Silver Knight Shield}
Shield of the Silver Knights of Anor Londo. A flowing canal is carved deep into its face.\\
The Silver Knights stayed behind in Anor Londo to defend the illusory goddess, and their shields are blessed with her divine protection.
\paragraph{Spiked Mace}
Choice weapon of the evangelists of the Cathedral of the Deep, mentors of the dwellers of the Undead Settlement.\\
Its long, sharp spikes cause great pain and bleeding.

\newpage
\part{Transposed Class Treasures}
\section*{Assassin}
\paragraph{Alva Armour}
Armor worn by Alva the Wayfarer. Light but offers very high defense.\\
Alva crossed many a land in search of a cure for Saint Serreta's sickness, but failed and relinquished his knighthood.\\
Alva was once wracked with guilt and remorse, but rediscovered his purpose in life with the aid of the witch who once plotted against him.
\paragraph{Carthus Curved Sword}
Curved sword of Carthus swordsmen.\\
This weapon's thick, heavy blade is crafted to cause bleeding, and requires ample strength and dexterity to wield effectively, suggesting that the swordsmen of Carthus were amongst the mightiest.
\paragraph{Elkhorn Round Shield}
Standard round wooden shield. The blue antlers are reminiscent of designs found in Mirrah.
Wooden shields are light, manageable, and offer relatively high magic absorption.
\paragraph{Lucerne}
Halberd with a large, hard beak-like protrusion. Inflicts thrust damage. Instead of thrusting like a spear, the wielder of the Lucerne aims to club the head with its hard beak.
\paragraph{Umbral Dagger}
A sharp dagger.\\
Crafted to facilitate assassinations with a focused backstab. One true strike with this blade, and your work will be done.
\section*{Herald}
\paragraph{Bountiful Light}
Miracle taught to knights of Gertrude, holy maiden to the Queen.\\
Gradually restores a large amount of HP.\\
The Heavenly Daughter is said to be the Queen's child.
\paragraph{Bountiful Sunlight}
Special miracle granted to the maidens of Gwynevere, Princess of the Sun. Gradual HP restoration for self and vicinity.\\
The miracles of Gwynevere, the princess cherished by all, grant their blessing to a great many warriors.
\paragraph{Grass Crest Shield}
Old medium metal shield of unknown origin. The grass crest is lightly imbued with magic, which slightly speeds stamina recovery.
\paragraph{Partizan}
Spear with a blade attached to a broad point. Boasts long reach, and can slice.\\
The wide range of this spear makes it adaptable to many situations. Its strength lies in its length, but in cramped quarters, this backfires, and slices ricochet off walls.
\paragraph{Saint Bident}
A silver bident decorated by a holy symbol, formerly wielded by Saint Klimt. He discarded this weapon, that draws upon one's faith, on the day that he put his own faith behind him.
\section*{Knight}
\paragraph{Black Iron Greatshield}
Greatshield of the mighty knight Tarkus.\\
Built of special black iron and even heavier than Knight Berenike's tower shield. Especially resistant to fire attacks and effective for shield bashing.
\paragraph{Elite Knight Armour}
Armor of a nameless knight, perhaps an elite knight of Astora, based on the fire-warding heraldic symbol on its blue surcoat.\\
Although he was loath to give up on his Undead mission, he perished at the Undead Asylum, and went Hollow.
\paragraph{Falchion}
Small curved sword. Each hit inflicts little damage, but fluid chain attacks are deadly.\\
The falchion's sharp slashing attacks are effective against cloth and flesh, but not against metal armor or tough scales.
\paragraph{Faraam Armour}
Armor blessed by the war god Faraam.\\
This armor is in the style of the Lion Knights, a once-mighty order from Forossa. Although the Lion Knights wore heavy armor, they were feared for their nimble two-handed swordplay.
\paragraph{Twin Dragon Greatshield}
A wooden greatshield featuring twin dragons.\\
Quite light for this size of shield.\\
One requires strength to handle a greatshield, but they are very stable. In battle, one fights using shield bash instead of parrying.
\section*{Warrior}
\paragraph{Balder Side Sword}
The knights of the ancient kingdom of Balder wielded these rock-solid, long swords which are excellent for thrust attacks.\\
Balder was the home of Knight King Rendal, but the kingdom was reduced to ruins after a widespread outbreak of Undead.
\paragraph{Dragonslayer's Axe}
Axe favored by Creighton the Wanderer, infamous deserter of the Knights of Mirrah.\\
Called Dragonslayer's Axe for the lightning that pulsates within its blade, but Creighton used it to slay men.
\paragraph{Fallen Knight Armour}
Armor of an order of fallen knights who disbanded and fled, but met untimely deaths.\\
The drab, tattered cloth conceals tough, black metal which provides dependable protection from fire. It is just possible to make out the majestic gold engravings on its surface.
\paragraph{Great Machete}
Created by strapping a large blade to a hilt. A crude makeshift weapon with low durability.\\
Primitive weapons can be more effective at evoking fear than more advanced efforts. Perhaps this is why the wielder chose this fearsome weapon.
\paragraph{Warpick}
Hammer with a large beak-shaped pommel. Originally a pickaxe; redesigned for battle.\\
This simple but deadly weapon hits heavily with thrust damage, such that it easily cracks metal armor.

\newpage
\part{Common Treasures}
\section*{Armours}
\paragraph{Black Armour}
Attire of hunters known as the King's Black Hands.\\
A black cape covers leather armor, shrouding the wearer in darkness.\\
Black Hand was a title established to honor hunters who served successive generations of kings. To date, no more than three such individuals have borne this distinction.
\paragraph{Court Sorcerer Robes}
Robe worn by court sorcerers of the Profaned Capital.\\
The formal gold stitching suggests they may have also been oracles.\\
There are many sorcerers who claim heirship to the great sage "Big Hat" Logan, and the Profaned Capital houses one of two leading schools.
\paragraph{Deacon Robes}
Robe worn by deacons of the Cathedral of the Deep. The deep red pigment denotes the blessing of fire.\\
In time, those dedicated to sealing away the horrors of the Deep succumbed to their very power. It seems that neither tending to the flame, nor the faith, could save them.
\paragraph{Drang Armour}
Armor of the Drang Knights, proclaimed descendants of the land known for the legend of the Linking of the Fire.\\
Fine protection that is both light and strong, having been reinforced with rare geisteel.\\
The Drang Knights were once feared sellswords, until treason meant descending into the abyss, and they were separated forever.
\paragraph{Exile Armour}
Armor of the watchdogs of Farron's Keep.\\
After the Legion's Watchers became Lords of Cinder, the wolf blood dried up, and Farron was consumed by a festering wood.\\
Within the wood, an emaciated old wolf commands watchdogs to defend the sanctity of sleeping warriors.\\
Both the exiles were surely watchdogs themselves, for Farron has always been a land of itinerants.
\paragraph{Firelink Armour}
Armor of the Soul of Cinder, a deific manifestation of the Lords of Cinder, who linked the First Flame.\\
It resembles a knight's armor, but bears hideous burns and contortions, taking the shape of a deathly ribcage.\\
It exists as a symbol of the great Lords and the noble act of linking the fire, though it is no more than an empty husk.
\paragraph{Hard Leather Armour}
Armor made of thick leather. Very common type of protective gear, it provides a sound level of defense.
\paragraph{Master’s Attire}
A terribly worn shirt.\\
Men are fond of weaving tales to explain the raggedness of their garb.\\
"My sixth sense warned me of danger, and I danced between flurries of blades, unscathed, but alas, my clothes went to tatters."
\paragraph{Sunless Armour}
Attire of a knight from the Sunless Realms, known for their resistance to both magic and the dark.\\
Metal plating and chainmail, treated with silver.\\
Sunless Knights serve the nameless moon, and perhaps it is for this reason the attire casts a feminine silhouette.
\paragraph{Sunset Armour}
Armor of Hodrick, holy knight of Sunless Realms.\\
This light gold armor, named for its sunset hues, is now faded and wrapped in tainted rags.\\
The sorry fool was known to wander the battlefield as a crazed ghoul, lashing out at friend and foe alike.
\paragraph{Worker Armour}
Garb worn by inhabitants of the Undead Settlement.\\
Official attire for the dissection and burial of undead. Naturally, the ceremonial significance of such work is long forgotten.\\
Indeed, no one could continue to entertain such horrors.
\section*{Weapons}
\paragraph{Brigand Axe}
Axe favored by brigands of a distant land.\\
Surprisingly sturdy battle axe that requires more strength to wield than a standard axe.
\paragraph{Claymore}
This larger type of greatsword is normally wielded with two hands due to its weight.\\
This highly flexible greatsword can be used to attack in swings or thrusts.
\paragraph{Great Axe}
This greataxe is a veritable mass of iron. Its weight sends foes flying, but it makes it difficult to handle without inhuman strength.\\
Any miss makes one very vulnerable, as each swing requires the full force of the body.
\paragraph{Great Mace}
Large mace wielded by the knights of the Cathedral of the Deep.\\
The extremely heavy strike attacks of this weapon are devastating and will break weaker shields with a single blow. Wielding such a weapon will require inhuman strength.
\paragraph{Halberd}
Long-hilted weapon mixing spear and axe is difficult to handle, requiring both strength and dexterity. The Halberd has two elementary attacks: spear-like thrusting and large sweeping swings. However, one false swing and the wielder is left wide open.
\paragraph{Morning Star}
Hammer with a sharp spike on its pommel. One of the more barbaric cleric weapons.\\
The effect of these spikes makes this strike-based weapon also cause bleeding.
\paragraph{Murakumo}
Giant curved sword forged using special methods in an Eastern land.\\
This unparalleled weapon cuts like a Katana but is heavier than a Nata machete. Requires extreme strength, dexterity, and stamina to wield.
\paragraph{Rapier}
Standard thrusting sword. Regular one-handed attack can be delivered with shield held up. Can parry with use of left hand.\\
Thrusting attacks pierce and are effective against foes with hard exteriors, but the wielder is left open to damage after a swing.
\paragraph{Reinforced Club}
A club with leather nailed to the pommel. The burg Undead merchant proudly peddles this club, but its reinforcement is shoddy. Indeed, its attack is stronger, but the club is no longer dependably sturdy.
\paragraph{Scimitar}
Small curved sword. Each hit inflicts little damage, but fluid chain attacks are deadly.\\
The scimitar's sharp slashing attacks are effective against cloth and flesh, but not against metal armor or tough scales.
\paragraph{Short Sword}
This small straight sword is widely used, to an extent only matched by the longsword.\\
An accessible sword which inflicts consistent regular damage and high slash damage, making it applicable to a variety of situations.
\paragraph{Silver Knight Straight Sword}
The silver knights of Anor Londo guard the city using this beautifully slender weapon.\\
Its chain attacks, in which the wielder takes great advancing steps and makes use of his bodyweight, are deadly even in single hits.
\paragraph{Sorcerer’s Staff}
Staff used to cast sorceries. A common catalyst given to sorcerers of the Vinheim Dragon School.\\
Equip a catalyst to use sorceries. Sorceries must be attuned at a bonfire before use.
\paragraph{Thrall Axe}
Small hand axe used by Lothric slaves.\\
A cunning weapon for a cunning lot, this axe is quick and deadly.
\paragraph{Winged Spear}
A long-hilted spear with a barbed point. Long reach, and can be used with shield up. Effective against hard exteriors, and hits for high damage at the right moment of an enemy's swing. But the hit radius is small, and it is easily blocked by shields.
\paragraph{Zweihander}
One of the gigantic straight greatswords.\\
As the name suggests, the Zweihander is held with two hands, but its wielder must still be inhumanly strong. It is this great weight that sends foes flying when hit solidly.
\section*{Shields}
\paragraph{Dragon Crest Shield}
Shield of a nameless knight, likely a high-ranked knight of Astora.\\
One of the enchanted blue shields. The dragon crest shield greatly reduces fire damage.
\paragraph{East-West Shield}
A wooden kite shaped shield. It is decorated with the ancient symbol of a double-headed eagle, painted yellow.\\
Wooden shields are lighter than metal shields, but with lower physical damage reduction, and reduced shield stability. <Paste>
\paragraph{Eastern Iron Shield}
A thick, round metal shield decorated with the unique crest of an eastern land.\\
Heaviest of the small shields, it is impressively weighty and thus able to deflect attacks with ease.
\paragraph{Effigy Shield}
Frightful occult shield. Defends against divine weapons and lightning.\\
In an ill-fated plot to destroy the very gods, the followers of the occult once attempted to steal the power of Gravelord Nito, the first of the dead.
\paragraph{Pierce Shield}
An unusual style of round shield peculiar to the knights of Catarina.\\
The center of the shield features a large, sharpened spike, which is used to skewer opponents.
\paragraph{Silver Eagle Kite Shield}
Orthodox metal shield engraved with a crest depicting a silver eagle.\\
Medium shields are the most average of shields, providing a practical balance of damage absorption, stability and weight.
\section*{Upgrade Materials}
\paragraph{Blessed Gem}
A gem of infused titanite. Commonly known as a charm kept by saints.\\
Used in infusion to create blessed weapons.\\
Special blessed weapons gradually restore HP and heavily damage reanimated foes.
\paragraph{Blood Gem}
A gem of infused titanite. Slurped by Irithyll slaves.\\
Used in infusion to create lacerating weapons.\\
Such weapons inflict lacerating damage. Most effective with sharp or spiked weapons.
\paragraph{Crystal Gem}
A gem of infused titanite. Introduced to Lothric by the Crystal Sages.\\
Used in infusion to create crystal weapons.\\
Crystal weapons inflict magic damage, and scale effectively with intelligence.
\paragraph{Heavy Gem}
A gem of infused titanite. Famously used to forge Farron greatswords.\\
Used in infusion to create heavy weapons.\\
A warrior can appreciate a heavy weapon, for they scale effectively with strength.
\paragraph{Lightning Gem}
A gem of infused titanite. Found in the aftermath of dragon hunts.\\
Used in infusion to create lightning weapons.\\
Lightning weapons inflict lightning damage, and scale with faith.
\paragraph{Poison Gem}
A gem of infused titanite. Discovered in the rotted forest of Farron.\\
Used in infusion to create poison weapons.\\
Such weapons inflict poison-laced damage that gradually eats away at foes.
\paragraph{Sharp Gem}
A gem of infused titanite. Forged the unique curved swords of Carthus.\\
Used in infusion to create sharp weapons.\\
A swordsman can appreciate a sharp weapon, for they scale effectively with dexterity.
\paragraph{Simple Gem}
A gem of infused titanite, said to be an object of infatuation for victims of stunted development.\\
Used in infusion to create simple weapons.\\
Simple weapons inflict magic damage and restore FP very gradually, to help even a simpleton muster some mettle.
\paragraph{Titanite Shard}
Titanite shard for weapon reinforcement. Most common titanite material.\\
Titanite shards are fragments of the Legendary Slabs. Titanite is etched into weapons to reinforce.
\section*{Miracles}
\paragraph{Force}
Common miracle among cleric knights. Creates shockwave.\\
This quickly-acting miracle inflicts no damage, but propels foes back and defends against arrows. Cleric knights use this miracle when charging into enemy mobs.
\paragraph{Heal}
Elementary miracle cast by clerics. Restores HP.\\
To cast a miracle, the caster learns a tale of the Gods, and says a prayer to be blessed by its revelations. Heal is the shortest of such miraculous tales.
\paragraph{Heal Aid}
Miracle imparted as charity to those of little faith.\\
Slightly restores HP.\\
To use miracles, equip a talisman or sacred chime and attune a miracle at a bonfire.
\section*{Pyromancies}
\paragraph{Fireball}
Standard pyromancy of the Great Swamp. Hurl fireball.\\
The fire damage caused by fireballs makes them effective against corporeal beasts and Undead, who by nature fear flame.
\paragraph{Poison Mist}
Unique pyromancy crafted by Eingyi, considered a heretic even at the Great Swamp. Create poison mist.\\
Eingyi became an egg-bearing Undead who serves a deformed young girl who speaks an unintelligible tongue.
\section*{Sorceries}
\paragraph{Great Magic Weapon}
Sorcery which improves upon Magic Weapon. High magic augmentation: right weapon.\\
At Vinheim Dragon School, only magic swordsmen on special orders are allowed to learn this spell which grants powerful augmentation to various weapons.
\paragraph{Soul Arrow}
Elementary sorcery. Fire a soul arrow.\\
Soul arrows inflict magic damage, making them effective against iron armor, tough scales, and other physically resilient materials.
\paragraph{Soul Stream}
Sorcery imparted by the first of the Scholars, when Lothric and the Grand Archives were but young.\\
Fires a torrential volley of souls.\\
The first of the Scholars doubted the linking of the fire, and was alleged to be a private mentor to the Royal Prince.
\section*{Misc.}
\paragraph{Chloranthy Ring}
The ring is named for its decorative green blossom, but its luster has long since faded. Raises stamina recovery speed.
\paragraph{Ember}
No Unkindled can ever truly claim the embers that burn within a champion's bosom, which is precisely what makes their yearning for warmth so keen.\\
Gain the strength of flame and increased max HP until death.\\
With the strength of fire, the summoning signs of Unkindled become visible, and seekers of embers can be summoned to join in co-operating. But beware, the embers may also attract invaders.
\paragraph{Firebombs}
Bisque urn filled with black powder. Explodes, inflicting fire damage.\\
Relatively powerful ranged weapon, especially in situations calling for fire damage. A very precious item for low levels.\\
Many warriors use these to augment their strategic repertoire.
\paragraph{Kukris}
Small throwing machete. Throw at enemies to cause bleeding damage.\\
A unique weapon originally used by swordsmen of Carthus, but now popular among bandits and thieves.

\part{Legendary Treasures}
\paragraph{Avelyn}
Repeating crossbow cherished by the weapon craftsman Eidas. Its elaborate design makes it closer to a work of art than a weapon. Intricate mechanism makes heavy damage possible through triple-shot firing of bolts, but in fact each bolt inflicts less damage.
\paragraph{Dark Sword}
Pitch-black straight sword of the Darkwraith, survivor of the land swallowed by darkness.\\
The Darkwraiths were the first red orb invaders, and originators of a unique sword technique inspired by their thick, broad blades.
\paragraph{Dragon Tooth}
Created from an everlasting dragon tooth. Legendary great hammer of Havel the Rock.\\
The dragon tooth will never break as it is harder than stone, and it grants its wielder resistance to magic and flame.
\paragraph{Drake Sword}
This Sword, one of the rare dragon weapons, is formed by a drake's tail. Drakes are seen as undeveloped imitators of the dragons, but in they are likely their distant kin.\\
The sword is imbued with a mystical power, to be released when held with both hands.
\paragraph{Fume Ultra Greatsword}
Ultra greatsword forged from the soul of the fume knight.\\
The exile swordsman Raime had the ability to expunge the black fog, but chose instead to live alongside it, in the company of the child of Dark that haunts this sword.
\paragraph{Gotthard Twinswords}
The hunters known as the King's Black Hands wielded paired weapons. These belonged to Gotthard, who fled the castle.\\
Gotthard rose quickly through the knighthood, no surprise to those who have witnessed his swordsmanship.
\paragraph{Moonlight Greatsword}
This sword, one of the rare dragon weapons, came from the tail of Seath the Scaleless, the pale white dragon who betrayed his own.\\
Seath is the grandfather of sorcery, and this sword is imbued with his magic, which shall be unleashed as a wave of moonlight.
\paragraph{Santier's Spear}
A spear that was embedded in a stone statue.\\
According to an old local legend, a great spear was used to defeat Santier, the walking statue. Perhaps this is that very spear...\\
But it will be difficult to utilize such a thing in the manner of a spear. Your only choice is to swing it around, and smite foes about the head.
\paragraph{Sunlight Straigth Sword}
This standard longsword, belonging to Solaire of Astora, is of high quality, is well-forged, and has been kept in good repair.\\
Easy to use and dependable, but unlikely to live up to its grandiose name.
\paragraph{Washing Pole}
Katana forged in an Eastern land. Very unusual specimen with a long blade.\\
The blade is extremely long, but as a result, quite easily broken.

\newpage
\part{Boss Treasures}
\section*{Boreal Outrider Knight}
\paragraph{Irithyll Rapier}
Thrusting sword bestowed upon the Outrider Knights of the Boreal Valley. This weapon is shrouded in frost, and causes frostbite.\\
Every Outrider Knight one day devolves into a beast, constantly hounded by Pontiff Sulyvahn's black eyes.
\paragraph{Irithyll Straight Sword}
Straight sword bestowed upon the Outrider Knights of the Boreal Valley. This weapon is enshrouded in frost, and causes frostbite.\\
Every Outrider Knight one day devolves into a beast, constantly hounded by Pontiff Sulyvahn's black eyes.
\paragraph{Outrider Armour}
Armor of an Irithyll outrider knight.
Enveloped in a dimly cool air.\\
The knights were given the eyes of the Pontiff, but the eyes transformed them into savage, raving warriors who only knew how to serve as mindless guards.
\section*{Gargoyle}
\paragraph{Gargoyle Tail Axe}
Sliced tail of the gargoyle guarding the Bell of Awakening in the Undead Church or patrolling Anor Londo.\\
Can be used as a bronze battle axe. Bends dramatically during large attacks, owing to its nature as a tail.
\paragraph{Gargoyle's Halberd}
Halberd of the gargoyle guarding the Bell of Awakening in the Undead Church.\\
Perfectly standard bronze halberd without any special power.
\paragraph{Gargoyle's Shield}
Bronze shield of the gargoyle guarding the Bell of Awakening in the Undead Church.\\
The gargoyle's skin is tough by itself, and perhaps its shield may have been a prop, for it is a rare example of a metal shield that does not reduce physical damage 100\%.
\section*{Titanite Demon}
\paragraph{Titanite}
Special titanite stolen from a faceless stone beast known as a Titanite Demon.\\
When the nameless blacksmith deity passed, from several Slabs, great beasts arose. The power of titanite remains within them, and they still roam Lordran today.
\paragraph{Titanite Catch Pole}
Weapon of the titanite demon, a faceless stone monster born from titanite slab. One of the enchanted weapons, perhaps from residual power of the titanite slab. Known for its leaping attack which comes smashing down on foes from above.
\section*{Winged Knight}
\paragraph{Winged Knight Armour}
Armor of the Winged Knights, named for their appearance, who swore themselves to the Angels.\\
Worship of the divine messengers was viewed as heresy in Lothric and unrecognized by any of the Three Pillars of rule.
\paragraph{Winged Knight Halberd}
Halberd wielded by the Winged Knights, who swore themselves to the Angels.\\
The thick, heavy, bloodstained blade can only be swung by one with inhuman strength.
\paragraph{Winged Knight Twin Axes}
Paired beheading axes wielded by the Winged Knights, who swore themselves to the Angels.\\
These axes, more befitting of an executioner than a knight, are indented to fit the human body.
\section*{Dancer of the Boreal Valley}
\paragraph{Dancer Armour}
Armor worn by the Dancer of the Boreal Valley.\\
The black eyes of the Pontiff eventually transformed the Dancer into a beastly creature, her armor fusing with her own hide.
\paragraph{Dancer's Enchanted Swords}
Paired enchanted swords that Pontiff Sulyvahn bestowed upon the Dancer of the Boreal Valley.
These blades, symbolic of the Dancer's vows, are enchanted with dark magic in the right-hand, and fire in the left, mirroring the Pontiff.
\paragraph{Soothing Sunlight}
Special miracle granted to the maidens of Gwynevere, Princess of the Sun. Restores high HP for self and vicinity.\\
The miracles of Gwynevere, the princess cherished by all, grant their blessing to a great many warriors.
\section*{Dragon Slayer Ornstein \& Executioner Smough}
\paragraph{Dragonslayer Armour}
Golden lion armor associated with Dragonslayer Ornstein, from the age of gods, and imbued with the strength of lightning.\\
In the dragonless age, this knight, who long guarded the ruined cathedral, left the land in search of the nameless king.
\paragraph{Dragonslayer Spear}
Cross spear born from the soul of Ornstein, a Dragonslayer guarding Anor Londo cathedral. Inflicts lightning damage; effective against dragons. Two-handed thrust relies on cross and buries spear deep within a dragon's hide, and sends human foes flying.
\paragraph{Smough's Armour}
Armor of Smough, the Executioner, protector of the cathedral at the forsaken city of Anor Londo. It offers extremely high defense and can be worn by humans, but not without great difficulty.
\paragraph{Smough's Hammer}
Great hammer from the soul of executioner Smough, who guards the cathedral in the forsaken city of Anor Londo. Smough loved his work, and ground the bones of his victims into his own feed, ruining his hopes of being ranked with the Four Knights.
\end{document}
